\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-11-04 Documents/M1/Astronum_2018/sections/TimeIntegration.tex
Some edtis on time integration

\subsection{Constraint-Preserving Implicit-Explicit Schemes}
Beyond the accuracy requirement, a convex-invariant IMEX scheme must satisfy additional constraints.
Our idea is finding the constraints on $a_{ij}$, $\tilde{a}_{ij}$, $\tilde{w}_{i}$, and $w_{i}$ that enable each $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ be convex combination of realizable moments:

@@

>>>>

\ee{Discuss GSA and Type~ARS here.}

\subsection{Constraint-Preserving Implicit-Explicit Schemes}

Beyond the accuracy requirement, a convex-invariant IMEX scheme must satisfy additional constraints.
Our idea is finding the constraints on $a_{ij}$, $\tilde{a}_{ij}$, $\tilde{w}_{i}$, and $w_{i}$ that enable each $\vect{u}^{(i)}$ and $\vect{u}^{n+1}$ be convex combination of realizable moments:

@@

\ee{Move definition of coefficients $c_{ij}$ and $\tilde{c}_{ij}$ here}
